   
   
\documentclass[11pt]{article}
\renewcommand{\baselinestretch}{1.05}
\usepackage{amsmath,amsthm,verbatim,amssymb,amsfonts,amscd, graphicx}
\usepackage{graphics}
\topmargin0.0cm
\headheight0.0cm
\headsep0.0cm
\oddsidemargin0.0cm
\textheight23.0cm
\textwidth16.5cm
\footskip1.0cm
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem*{surfacecor}{Corollary 1}
\newtheorem{conjecture}{Conjecture} 
\newtheorem{question}{Question} 
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\usepackage{graphicx}
\graphicspath{ {images/} }
 \begin{document}
 


\title{Homework 3}
\author{Jeremy Desser}
\begin{titlepage}
\maketitle
\end{titlepage}


\section*{15.26}
\subsection*{a.}
\subsection*{i.} $A \rightarrow B $ Does not hold.
\subsection*{ii.} $B \rightarrow C $ Dependancy holds.
\subsection*{iii.} $C \rightarrow B $ Does not hold.
\subsection*{iv.} $B \rightarrow A $ Dependancy holds.
\subsection*{v.} $C \rightarrow A $ Does not hold.


\subsection*{b.}
 Since a candidate key  is a set of attributes $x$ such that $x \rightarrow ABC$, x can only be B, thus B is the only candidate key.
\section*{15.28} 


\section*{15.31} 
\subsection*{a.}
The Books relation is in 1NF since book title \rightarrow book\_type and book\_ type ->List\_ price\\
\subsection*{b.}
2NF:\\
    book1(Book\_title, Authorname)\\
    book2(Book\_title, Publisher, Book\_type, Listprice)\\
    book3(Authorname, Author\_ affil)\\
    3NF:\\
    book1(Book\_title, Authorname)\\
    book2(Book\_title, Publisher, Book\_ type)\\
    book3(Book\_title, list\_ price)\\
    book4(Authorname, Author\_ affil)\\
    BCNF:\\
book1(Book\_title, Authorname)\\
    book2(Book\_title, Publisher)\\
book3(Book\_title, Book\_ type)\\
    book4(Book\_title, list\_ price)\\
    book5(Authorname, Author\_ affil)\\
\section*{16.28}
Input: A universal relation R and a set of functional dependencies F on the attributes of R .\\
Set D := { R } ; \\
While there is a relation schema Q in D that is not in BCNF \\
do \\
{ 
choose a relation schema Q in D that is not in BCNF; \\
find a functional dependency X → Y in Q that violates BCNF;\\
replace Q in D by two relation schemas ( Q – Y ) and ( X ∪ Y ); \\
} ;
$R = {A, B, C, D, E, F, G, H, I} $\\
$D= R$\\
$F = { {A, B} -> {C}, {A} -> {D, E}, {B} -> {F}, {F} ->{G, H}, {D} -> {I, J} }$\\

$Q1 = {A,D,E,I,J}$\\
$Q1-Y1 = {A,D,E}$\\
$X1 U Y1 = {D,I,J}$\\

$Q2 = {B,F,G,H}$\\
$Q2-Y2 = {B,F}$\\
$X2 U Y2 = {F,G,H}$\\
$D = {Q1-Y1 = {A,D,E}$\\
$X1 U Y1 = {D,I,J}$\\
$Q2-Y2 = {B,F}$\\
$X2 U Y2 = {F,G,H} }$\\
$G = {{ A , B } → { C }, { B , D } → { E , F }, { A , D } → { G , H }, { A } → { I }, { H } → { J } }$\\
$Q1 = {A,D,G,H,J,I}$\\
$Q1-Y1 = {AGH}$\\
$X1 U Y1 = {AI}$\\
$Q2-Y2={A,D,H,J}$\\
$Q2-Y2={A,D,H}$\\
$X2 U Y2 = {H,J}$\\
$Q3 = {B,D,E,F}$\\

\section*{28.15}
There is only one frequent itemset of size 3, {milk,bread,eggs}.  We can try the rule milk,eggs -> bread.  The confidence of this rule  is 0.3/0.3 which is higher than the min confidence value of 0.7.  We can also try is bread -> milk,eggs.  The confidence of this rule is 0.3/0.4 which again is higher than the required minimum confidence.\\


\end{document}